Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-09-25 GWLDCII.tex
my part from the notes file

@@

@@

We make one further simplification in order to eliminate the possibility that $n-2 \in I_{n-2}^V$ but $n-1 \not\in I_{n-2}^V$, which can only occur if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports no propagators other than $p$. In this situation, apply the dihedral transformation that reflects $W$ along the line perpendicular to the $(n-2){th}$ edge, so that $p$ is unchanged but $q = (n-1,1)$ in the new diagram. The new diagram is an example of Case 1, {\color{violet} i.e. satisfying $n-2 \not \in I_{n-2}^V$}. \sanote{pull this simplification out ealier (before 4.10), so that when I'm counting cases, I'm not confused as to why this one hasn't been covered.}

In summary, $W$ is a diagram with one of the two configurations depicted in Figure~\ref{fig special p}, and if $n-2 \in I_{n-2}^V$ then $n-1 \in I_{n-1}^V$ as well. Let $V$ be $W$ with $p$ removed.

@@

  Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus: we will view these as the three ``new'' plusses required by the induction step and use Lemmas~\ref{lem n and n-1} through \ref{lem other k} to construct a pairing between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row. See Figure~\ref{fig:le diagrams bijection}.

@@

  \end{itemize}
The first three points follow immediately from Lemmas \ref{lem n and n-1} through \ref{lem other k}. If $n-2 \not\in I_{n-2}^V$ by Lemma~\ref{lem n-2 good} there are no plusses in column $n-2$ of the diagram of $V$, and all plusses have been accounted for. If $n-2 \in I_{n-2}^V$ then we are in the setting of Lemma~\ref{lem n-2 bad}, and there is exactly one plus in column $n-2$ of the diagram of $V$; it is paired with the one plus in $W$ yet unaccounted for, as described in points 4 and 6 of that lemma.

>>>>

The next several lemmas assume $V$ and $W$ to be as above. They discuss how the shape of the Le diagram changes from $V$ to $W$ and how the plusses in $V$ shift to become plusses in $W$. In particular, the Le diagram for $W$ has an extra row with three columns labeled by $n-3$ (see Figure \ref{fig Le} and Lemma \ref{lem shape}). This last row contains three (new) plusses. All other plusses in the Le diagram of $V$ shift in a predictable manner to become plusses in the Le diagram of $W$. (See Lemmas \ref{lem n and n-1} to Theorem \ref{thm dim}.

We proceed to address the cases laid out in \ref{lem I}, getting the shape of the Le diagram of $W$ from the relation $I_n^W= I_n^V \cup {n-3}$.

@@

In the next two lemmas, we consider the plusses contributed to the Le diagram of $W$ by $I_{n-2}^W$.

\begin{rmk}\label{rem n-2 case} Note that we need not consider the case when $n-2 \in \in I_{n-2}^V$ but $n-1 \not\in I_{n-2}^V$ laid out in Lemma \ref{lem I}. This case can only occur if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports no propagators other than $p$. In this situation, apply the dihedral transformation that reflects $W$ along the line perpendicular to the $(n-2)^{th}$ edge, so that $p$ is unchanged but $q = (n-1,1)$ in the new diagram. The new diagram is an example of Case 1, i.e. satisfying $n-2 \not \in I_{n-2}^V$. Therefore, for the rest of this section, we only consider the situation where if $n-2 \in I_{n-2}^V$ then $n-1 \in I_{n-1}^V$. 
\end{rmk}

@@

%We make one further simplification in order to eliminate the possibility that $n-2 \in I_{n-2}^V$ but $n-1 \not\in I_{n-2}^V$, which can only occur if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports no propagators other than $p$. In this situation, apply the dihedral transformation that reflects $W$ along the line perpendicular to the $(n-2){th}$ edge, so that $p$ is unchanged but $q = (n-1,1)$ in the new diagram. The new diagram is an example of Case 1, {\color{violet} i.e. satisfying $n-2 \not \in I_{n-2}^V$}. \sanote{pull this simplification out ealier (before 4.10), so that when I'm counting cases, I'm not confused as to why this one hasn't been covered.}

Note that by Remark \ref{rem n-2 case}, we only need to consider when $W$ is a diagram with one of the two configurations depicted in Figure~\ref{fig special p}, and if $n-2 \in I_{n-2}^V$ then $n-1 \in I_{n-1}^V$ as well. Let $V$ be $W$ with $p$ removed.

@@

  Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus, i.e. there are plusses in the positions $(n-3) \rightarrow (n-2)$, $(n-3) \rightarrow (n-1)$ and $(n-3) \rightarrow n$. We will view these as the three ``new'' plusses required by the induction step and use Lemmas~\ref{lem n and n-1} through \ref{lem other k} to construct a pairing between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row. See Figure~\ref{fig:le diagrams bijection}.

@@

  \end{itemize}
The first three points follow immediately from Lemmas \ref{lem n and n-1} through \ref{lem other k}. If $n-2 \not\in I_{n-2}^V$ by Lemma~\ref{lem n-2 good} there are no plusses in column $n-2$ of the diagram of $V$, and all plusses have been accounted for. If $n-2 \in I_{n-2}^V$ then we are in the setting of Lemma~\ref{lem n-2 bad}, and there is exactly one plus in column $n-2$ of the diagram of $V$; it is paired with the one plus in $W$ yet unaccounted for: namely those in positions $(n-5) \rightarrow n$ or $(n-5) \rightarrow (n-1)$, as described in points 4 and 6 of that lemma.
